Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-08-27 manuscript/manuscript.tex
Amending manuscript (fixes #143)

\begin{figure}
\includegraphics{figure_3}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone:
(a) The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b) PCCA++ identifies as five metastable states.
(c) The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states, in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d) the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that states $\mathcal{S}_{(1,3,5)}$ act as a transition region between states $\mathcal{S}_2$ and $\mathcal{S}_4$.
(e) The Trp-1 SASA autocorrelation function yields a weak signal (top) which, however, can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$ (bottom).}
\label{fig:msm-analysis}
\end{figure}

@@

@@

As an example, here we look at the fluorescence correlation of Trp-1, since this terminal tryptophan is a realistic experimental observable for our pentapeptide system.
In order to compute the fluorescence correlation functions we require a microscopic, instantaneous value of the tryptophan fluorescence for each of the original $75$ MSM microstates.
To approximate the fluorescence signal in our pentapeptide system, we use the mdtraj library~\cite{mdtraj} to compute the solvent accessible surface area (SASA) of Trp-1.
Now that we have an approximation of the fluorescence in each of our MSM states, we can use PyEMMA to compute the fluorescence autocorrelation function (ACF) from our MSM (\ref{fig:msm-analysis}e, upper).
Note how the computed ACF has a very small response (i.e., signal amplitude).

Using PyEMMA, we can simulate the relaxation of an observable if we had prepared our molecular system in a nonequilibrium initial condition.
The experimental counterpart of such a prediction could be a temperature or pressure jump experiment or a stopped flow assay.
To illustrate such an experiment, we initialize our molecular ensemble as the metastable distribution of $\mathcal{S}_1$ and follow the predicted fluorescence signal as it relaxes to equilibrium (\ref{fig:msm-analysis}e, lower).
We see that the predicted relaxation signal has a much larger amplitude for the nonequilibrium initialization, making it more likely to be experimentally measurable.

>>>>

\begin{figure}
\includegraphics{figure_3}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone:
(a) The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b) PCCA++ identifies as five metastable states.
(c) The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states, in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d) the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that states $\mathcal{S}_{(1,3,5)}$ act as a transition region between states $\mathcal{S}_2$ and $\mathcal{S}_4$.}
\label{fig:msm-analysis}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_5}
\caption{The Trp-1 SASA autocorrelation function yields a weak signal (a) which, however, can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$ (b). The solid/orange lines denote the maximum likelihood MSM result; the dashed/blue lines and the the shaded areas indicate sample means and $95\%$ confidence intervals computed with a Bayesian sampling procedure.}
\label{fig:msm-exp-obs}
\end{figure}

@@

As an example, here we look at the fluorescence correlation of Trp-1, since this terminal tryptophan is a realistic experimental observable for our pentapeptide system.
In order to compute the fluorescence correlation functions we require a microscopic, instantaneous value of the tryptophan fluorescence for each of the original $75$ MSM microstates.
To approximate the fluorescence signal in our pentapeptide system, we use the mdtraj library~\cite{mdtraj} to compute the solvent accessible surface area (SASA) of Trp-1.
Now that we have an approximation of the fluorescence in each of our MSM states, we can use PyEMMA to compute the fluorescence autocorrelation function (ACF) from our MSM (\ref{fig:msm-exp-obs}a).
Note how the computed ACF has a very small response (i.e., signal amplitude).

Using PyEMMA, we can simulate the relaxation of an observable if we had prepared our molecular system in a nonequilibrium initial condition.
The experimental counterpart of such a prediction could be a temperature or pressure jump experiment or a stopped flow assay.
To illustrate such an experiment, we initialize our molecular ensemble as the metastable distribution of $\mathcal{S}_1$ and follow the predicted fluorescence signal as it relaxes to equilibrium (\ref{fig:msm-exp-obs}b).
We see that the predicted relaxation signal has a much larger amplitude for the nonequilibrium initialization, making it more likely to be experimentally measurable.
